Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-09 prop.tex
prop.tex \section{Introduction} Add citation...

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and
computations are processes bounded in space, time, energy, and other
resources. Yet, for centuries, the mathematical formalization of such
processes has been founded on the infinitely precise real or complex
numbers. Indeed, almost every description of quantum mechanics,
quantum computation, or quantum experiments refers to entities such as
$e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective, such
numbers do not exist in their entirety ``for free.''  For example, the
state of the art algorithms for computing the $n$th binary digit of~$\pi$
require on the order of $O(n\log^{O(1)}(n))$
operations~\cite{journals/moc/BaileyBP97}. In other words, simply
referring to the $n$th digit of $\pi$ requires more and more resources
as $n$ gets larger. Taking such resource bounds into consideration is
what founded computer science as a discipline and is crucial for
understanding the very nature of computation and, following
Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.

>>>>

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Kent1999,CliftonKent2000}.
Indeed, almost every description of quantum mechanics, quantum computation,
or quantum experiments refers to entities such as $e$, $\pi$, $\sqrt{2}$,
etc. From a computational perspective, such numbers do not exist in
their entirety ``for free.'' For example, the state of the art algorithms
for computing the $n$th binary digit of~$\pi$ require on the order
of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
In other words, simply referring to the $n$th digit of $\pi$ requires
more and more resources as $n$ gets larger. Taking such resource
bounds into consideration is what founded computer science as a discipline
and is crucial for understanding the very nature of computation and,
following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.
